Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-24 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

@@

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
of the prefect prediction, a cryptodeterministic measure can model
the belief of an event which has already happened. For example, if
we toss the coin in example~\ref{ex1}, and see $HH$, our belief
of which event has happened can be model by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
it was a famous question whether quantum mechanics have any change
to be improved and predict perfectly. One of the ``no'' answer was
due to the Kochen-Specker theorem.

>>>>

Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

@@

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
of the prefect prediction, a cryptodeterministic measure can model
the belief of events which has already happened. For example, if we
toss the coin in example~\ref{ex1}, and see $HH$, our belief of
which event has happened can be model by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
it was a famous question whether quantum mechanics have any change
to be improved and predict unambiguously, rather than probabilistic.
One of the ``no'' answer was due to the Kochen-Specker theorem.
